\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/intro.tex
vfill for intro
fixed typos

%!TEX root = sui14.tex
\section{Introduction}
%\bjoern{We should see if we can change language in a few places to strengthen the connection to ``Spatial User Interaction", the title of the conference.}

%% from the swarm vision to the necessity of selection
The number of smart objects in our environment with embedded computation and communication has grown rapidly. These objects are all potential targets for interaction. To initiate {\em spatial interactions}, a user needs to first acquire the target object -- a fundamental task that has been extensively studied in graphical user interfaces, but is not yet well-explored in {\em physical spaces}.

%\sean{Ben mentioned about discussing the limitations of list approach. Below is the paragraph from chi submission for your reference.}
%
\changes{Today, commercial solutions for controlling physical devices (such as Belkin WeMo) use smartphones as {\em universal remote controls} -- users first browse a list of all available devices and then call up a device-specific user interface. This method faces {\em naming} issues (where is ``Light 4 in Area E''?) and {\em scaling} issues as the number of controlled devices increases.}
%
%% previous approaches are limited
Past research has used direct aiming at target devices in space with phones to overcome these problems~\cite{beigl_point_1999,patel_2-way_2003}. In such techniques, the aiming device first has to be retrieved (e.g., from a pocket); user's hands have to be free for operation; and the user's visual attention is split between looking down at a screen and out at targets in the world.

@@

Our {\em Intensity IR} techniques improves refinement as target objects compare received IR signal strength (RSS). This value allows the system to eliminate some peripheral targets and to re-order the refinement interface's list by their intensity values. For example, in Figure~\ref{fig:teaser} of {\em Intensity IR} technique, device 5 is eliminated first and the list is re-ordered based on the intensity readings. A second study with $10$ participants shows that {\em Intensity IR} successfully reduces both the probability of needing to do refinement as well as the time spent in list navigation when compared to {\em Naive IR}.

>>>>

%!TEX root = sui14.tex
\vfill
\section{Introduction}
%\bjoern{We should see if we can change language in a few places to strengthen the connection to ``Spatial User Interaction", the title of the conference.}

%% from the swarm vision to the necessity of selection
The number of smart objects in our environment with embedded computation and communication has grown rapidly. These objects are all potential targets for interaction. To initiate {\em spatial interactions}, a user needs to first acquire the target object -- a fundamental task that has been extensively studied in graphical user interfaces, but not yet well-explored in {\em physical spaces}.

%\sean{Ben mentioned about discussing the limitations of list approach. Below is the paragraph from chi submission for your reference.}
%
\changes{Today, commercial solutions for controlling physical devices (such as Belkin WeMo) use smartphones as {\em universal remote controls} -- users first browse a list of all available devices and then call up a device-specific user interface. This method faces {\em naming} issues (where is ``Light 4 in Area E''?) and {\em scaling} issues as the number of controlled devices increases.}
%
%% previous approaches are limited
Past research has used direct aiming at target devices in space with phones to overcome these problems~\cite{beigl_point_1999,patel_2-way_2003}. Such techniques have a few drawbacks: the aiming device first has to be retrieved (e.g., from a pocket); user's hands have to be free for operation; and the user's visual attention is split between looking down at a screen and out at targets in the world.

@@

Our {\em Intensity IR} technique improves refinement as target objects compare IR received signal strength (RSS). This value allows the system to eliminate some peripheral targets and to re-order the refinement interface's list by their intensity values. For example, in Figure~\ref{fig:teaser} of {\em Intensity IR} technique, device 5 is eliminated first and the list is re-ordered based on the intensity readings. A second study with $10$ participants shows that {\em Intensity IR} successfully reduces both the probability of needing to do refinement as well as the time spent in list navigation when compared to {\em Naive IR}.
